Revisiting the Austral Spring Extratropical Southern Hemisphere zonally asymmetric circulation using complex Empirical Orthogonal Functions

### 2022-04-20 analysis/paper/shceof.Rmd
Quita ggthemes y gg4hx

library(metR)
library(data.table)
library(magrittr)
library(ggplot2)
library(tagger)
library(ggperiodic)
library(patchwork)
library(kableExtra)
library(shceof)

@@

era_more %>%
  copy() %>% 
  .[, ref := year(time) > 1979] %>% 
  # .[, hgt := scale(hgt, center = FALSE, scale = sd(hgt[ref])), by = .(part, cEOF)] %>%
  ggplot(aes(time, hgt*1e3)) +
  # Zero line + rangeframe
  geom_hline(data = ~.x[, mean(hgt)*1e3, by  = .(cEOF, part)], 
             aes(yintercept = V1), size = 0.2, color = "gray30") +
  ggthemes::geom_rangeframe(sides = "r", size = 0.2, color = "gray30") +
  geom_line(aes(color = part)) +
  geom_point(aes(color = part), size = 0.25) +
  # geom_line(data = era_less) +
  scale_alpha_manual(values = c(1, 0.2)) +
  geom_smooth(method = "lm", aes(color = stage(part, after_scale = scales::muted(color))),
              show.legend = FALSE, size = 0.8) +
  scale_x_date(NULL, date_labels = "%Y",
               breaks = seq(as.Date("1950-01-01"),
                            as.Date("2020-01-01"), by = "10 years"),
               minor_breaks = seq(as.Date("1950-01-01"),
                                  as.Date("2020-01-01"), by = "2 years")) +
  scale_y_continuous(NULL, minor_breaks = NULL, sec.axis = dup_axis()) +
  scale_color_brewer(NULL, palette = "Dark2", 
                     guide = guide_legend(override.aes = list(fill = NA))) +
  facet_grid(cEOF ~ part) +
  theme(panel.spacing = grid::unit(1.5, "lines"),
        strip.placement = "outside", 
        panel.grid.minor.x = element_line(linetype = 2))  +
  tag_facets("rc") +
  panel_background 
```

@@

  if (length(which_cEOF) > 1) {
    facet <- ggh4x::facet_nested(cEOF ~  term)
  } else {
    facet <- ggh4x::facet_nested(lev ~ cEOF +  term, 
                                 labeller = labeller(lev = lab_lev))
  }

@@

    scale_x_longitude(labels = NULL) +
    scale_y_latitude(labels = NULL,
                     minor_breaks = NULL) +
    grid_y +
    facet +
    geom_coords() +
    coord_polar() +
    tag_facets("rc")
}

>>>>

library(metR)
library(data.table)
library(magrittr)
library(ggplot2)
library(tagger)
library(ggperiodic)
library(kableExtra)
library(shceof)

@@

era_more %>%
  copy() %>% 
  .[, ref := year(time) > 1979] %>% 
  # .[, hgt := scale(hgt, center = FALSE, scale = sd(hgt[ref])), by = .(part, cEOF)] %>%
  ggplot(aes(time, hgt*1e3)) +
  # Zero line + rangeframe
  geom_hline(data = ~.x[, mean(hgt)*1e3, by  = .(cEOF, part)], 
             aes(yintercept = V1), size = 0.2, color = "gray30") +
  geom_segment(data = ~.x[, .(min = min(hgt)*1e3,
                              max = max(hgt)*1e3), by  = .(cEOF, part)],
               aes(x = structure(Inf, class = "Date"),
                   xend = structure(Inf, class = "Date"),
                   y = min,
                   yend = max), size = 0.2, color = "gray30") +
  geom_line(aes(color = part)) +
  geom_point(aes(color = part), size = 0.25) +
  # geom_line(data = era_less) +
  scale_alpha_manual(values = c(1, 0.2)) +
  geom_smooth(method = "lm", aes(color = stage(part, after_scale = scales::muted(color))),
              show.legend = FALSE, size = 0.8) +
  scale_x_date(NULL, date_labels = "%Y",
               breaks = seq(as.Date("1950-01-01"),
                            as.Date("2020-01-01"), by = "10 years"),
               minor_breaks = seq(as.Date("1950-01-01"),
                                  as.Date("2020-01-01"), by = "2 years")) +
  scale_y_continuous(NULL, minor_breaks = NULL, sec.axis = dup_axis()) +
  scale_color_brewer(NULL, palette = "Dark2", 
                     guide = guide_legend(override.aes = list(fill = NA))) +
  facet_grid(cEOF ~ part) +
  theme(panel.spacing = grid::unit(1.5, "lines"),
        strip.placement = "outside", 
        panel.grid.minor.x = element_line(linetype = 2))  +
  tag_facets("rc") +
  panel_background 
```

@@

  if (length(which_cEOF) > 1) {
    stop("More than one ceof")
  }

@@

    scale_x_longitude(labels = NULL) +
    scale_y_latitude(labels = NULL,
                     minor_breaks = NULL) +
    grid_y +
    facet_grid(lev ~ term, 
               labeller = labeller(lev = lab_lev)) +
    geom_coords() +
    coord_polar() +
    tag_facets("rc") +
    labs(title = which_cEOF) +
    theme(plot.title = element_text(hjust = 0.5, size = theme_get()$strip.text$size))
}
